Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers

### 2019-02-25 reports/paper.tex
final of paper

\begin{abstract}
In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and an ionic solvent.
Deep eutectic solvents are a novel class of environmentally friendly, non-aqueous, room temperature liquids with tunable properties, that have wide-ranging potential applications and are capable of promoting the self-assembly of surfactant molecules.
We use a chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show that these monolayers broadly behave as they do on water.
This method allows for the monolayer structure to be determined, alongside the molecular volumes of the individual monolayer components, without the need for water-specific constraints to be introduced.
Furthermore, using this method we are able to better understand the correlations present between parameters in the analytical model.
This example of a non-aqueous phospholipid monolayer has important implications for the potential uses of these solvents and for our understanding of how biomolecules behave in the absence of water.
  \begin{description}
  \item[Usage]
  Electronic Supplementary Information (ESI) available: All analysis/plotting
  scripts and figure files, allowing for a fully reproducible, and automated,
  analysis workflow for the work presented is available at
  \url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.2538002)
  under a CC BY-SA 4.0 license.
  Reduced experimental datasets are available at
  \url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
  \end{description}
\end{abstract}
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

@@

\subsection{Methods}
%
XRR measurements were taken on I07 at Diamond Light Source, at \SI{12.5}{\kilo\electronvolt} photon energy using the double-crystal deflector \cite{arnold_implementation_2012}.
The reflected intensity was measured in a momentum transfer range from \SIrange{0.018}{0.7}{\per\angstrom}.
The data were normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
Samples were equilibrated for at least one hour and preserved under an argon atmosphere to minimise the adsorption of water by the subphase.
XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: \SIlist[list-units = single]{20;25;30;35}{\milli\newton\per\meter}, DMPC: \SIlist[list-units = single]{20;25;30;40}{\milli\newton\per\meter}, DPPC: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, DMPG: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, as measured with an aluminium Wilhelmy plate; measurements were conducted at \SIlist{7;22}{\celsius}.
The aluminium Wilhelmy plate was used over a traditional paper plate due to the low wettability of paper by the DES.

@@

In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evolution method available to refnx from the scipy library \cite{jones_scipy_2001}, to find the parameters that gave the best fit to the data.
The parameter space was then probed using the MCMC method available through emcee \cite{foreman-mackey_emcee_2013}, which allowed for an estimate of the probability distribution function (PDF) associated with each parameter.
In the MCMC sampling, 200 walkers were used over 1000 iterations, following equilibration of 200 iterations.
The use of MCMC sampling allowed for the Bayesian inference of the PDF for each of the variables and their respective interactions.
The Shapiro test to be used to assess if each PDF was normally distributed.
Parameters that were shown to be normally distributed are given with symmetric confidence intervals, while those that failed the Shapiro test are given with asymmetric confidence intervals (\SI{95}{\percent} confidence intervals in both cases).
However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, i.e. they do not account of systematic uncertainty in the measurement that is underrepresented, or unrepresented, in the experimental dataset.

%
\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/dlpc_ref_sld}
    \includegraphics[width=0.45\textwidth]{figures/dmpc_ref_sld}
    \includegraphics[width=0.45\textwidth]{figures/dppc_ref_sld}
    \includegraphics[width=0.45\textwidth]{figures/dmpg_ref_sld}
    \caption{\small The XRR profiles (left) and SLD profiles (right) for each
  of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, and (d) DMPG, at the four
  measured surface pressures; see legend above each plot. The different
  surface pressure XRR profiles have been offset in the $y$-axis by an order
  of magnitude and SLD profiles offset in the $y$-axis by
  \SI{5e-6}{\per\square\angstrom}, for clarity.}
    \label{fig:lipids}
\end{figure}
%
\section{Results \& Discussions}
%
The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid.
Although lipid monolayers on water often reach values above \SI{50}{\milli\newton\per\meter}, signifying a decrease in surface tension of ca. \SI{20}{\milli\newton\per\meter} upon addition of lipid, it was not possible to reach those values for the monolayers on DES \cite{mohwald_phospholipid_1990}.
The surface tension of pure choline chloride:glycerol has been previously reported to be \SI{63.5\pm0.5}{\milli\newton\per\meter} \cite{sanchez-fernandez_micellization_2016}.
This means that a surface pressure of ca. \SI{40}{\milli\newton\per\meter} in choline chloride:glycerol will be reached with a reduction of ca. \SI{20}{\milli\newton\per\meter} in the surface tension.
Interestingly, the absolute values of surface tension reduction in both water and choline chloride:glycerol upon addition of lipid are similar.
Therefore, surface pressures of up to \SI{40}{\milli\newton\per\meter} were measured for the monolayers on DES, when possible.
The resulting XRR profiles and associated SLD profiles are shown in Figure \ref{fig:lipids}.
Table \ref{tab:liptab} gives details of all varied parameters for each lipid at \SI{30}{\milli\newton\per\meter}, as well as the details of $\phi_h$ which was determined from Eqn. \ref{equ:phih} (the same details for the other surface pressures are available in Section \ref{sec:xrrpara} of the ESI).
%
\begin{table*}
    \caption{\label{tab:liptab} The best-fit values, and associated \SI{95}{\percent} confidence intervals for the varying parameters in the XRR models, at the \SI{30}{\milli\newton\per\meter}. The values for $\phi_h$ was obtained from the appropriate use of Eqn. \ref{equ:phih}.}
  \begin{ruledtabular}
    \begin{tabular*}{\textwidth}{ccccc}
    Lipid & DLPC & DMPC & DPPC & DMPG \\
    \hline
    $\sigma$/\si{\angstrom} & \input{../output/dlpc/rough30.txt} & \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
    $d_t$/\si{\angstrom} & \input{../output/dlpc/tail30.txt} & \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
    \hline
    $V_t$/\si{\cubic\angstrom} & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
    $V_h$/\si{\cubic\angstrom} & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
    $d_h$/\si{\angstrom} & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} & \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
    \end{tabular*}
  \end{ruledtabular}
\end{table*}
%

Following the initial structural determination of the monolayer by XRR, NR was used to confirm the structure and show the applicability of the chemically-consistent model for DPPC and DMPC.
The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron} (the other NR and SLD profiles can be found in Figure \ref{fig:sineutron} of the ESI).
Table \ref{tab:neutron} gives details of the varied parameters at each surface pressure as well as $\phi_h$ as determined from NR.
%
\begin{figure}
    \centering
  \includegraphics[width=0.45\textwidth]{figures/dmpc_20n_ref_sld}
    \includegraphics[width=0.45\textwidth]{figures/dppc_20n_ref_sld}
    \caption{\small The NR and SLD profiles at a surface pressure of
  20 mNm$^{-1}$ for two contrasts, the solid line identifing the hdDES contrast and the dashed line the hDES contrast; (a) DMPC, (b) DPPC. The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
    \label{fig:neutron}
\end{figure}
%
%
\begin{table*}
  \caption{\label{tab:neutron} The best-fit values, and associated 95 \%
  confidence intervals for the varying parameters in the co-refined NR models.
  The values of $\phi_h$ were found using Eqn. \ref{equ:phih}.}
  \begin{ruledtabular}
    \begin{tabular*}{\textwidth}{ccccc}
    Lipid & \multicolumn{2}{c}{d$_{54}$-DMPC} & \multicolumn{2}{c}{d$_{62}$-DPPC} \\
    SP/mNm$^{-1}$ & 20 & 25 & 15 & 20 \\
    \hline
    $\sigma_{t,h,s}$/\si{\angstrom} & \input{../output/dmpc/rough20_neutron.txt} & \input{../output/dmpc/rough25_neutron.txt} & \input{../output/dppc/rough15_neutron.txt} & \input{../output/dppc/rough20_neutron.txt} \\
    $d_t$/\si{\angstrom} & \input{../output/dmpc/tail20_neutron.txt} & \input{../output/dmpc/tail25_neutron.txt} & \input{../output/dppc/tail15_neutron.txt} & \input{../output/dppc/tail20_neutron.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh20_neutron.txt} & \input{../output/dmpc/solh25_neutron.txt} & \input{../output/dppc/solh15_neutron.txt} & \input{../output/dppc/solh20_neutron.txt} \\
    \end{tabular*}
  \end{ruledtabular}
\end{table*}
%
\subsection{Effect of compression on monolayer thickness}
%
From Tables \ref{tab:liptab} and \ref{tab:neutron}, we can see that, as expected and as found in previous work \cite{mohwald_phospholipid_1990,vaknin_structural_1991}, the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$~\si{\angstrom} at \SI{30}{\milli\newton\per\meter} \cite{johnson_structure_1991} in water for DMPC, and \input{../output/dppc/tail30.txt}~\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=16.7$~\si{\angstrom} at \SI{40}{\milli\newton\per\meter} \cite{helm_phospholipid_1987} in water for DPPC.

@@

\subsection{Solvent effect on lipid head component volumes}
%
Figure \ref{fig:lipresults} shows the PDFs determined for the head component volume for each of the four lipids.
The three lipids with the PC head component are consistent, giving values of $\sim330$ \AA$^3$, regardless of tail component.
This agrees well with the values found for the same head component in water, shown in Table \ref{tab:water}.
Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}~\si{\angstrom\cubed}.
The PG head component volume in water, from either DMPG using differential vibrating tube densimetry \cite{pan_molecular_2012} or POPG using molecular dynamics simulations \cite{kucerka_scattering_2012}, is noticeably smaller.
This indicates that there may be some effect arising from the solvation in choline chloride:glycerol causing an apparent increase in the PG component volume when compared with water.
However, as this has only been shown for a single PG-lipid at the air-DES interface.

@@

A physically and chemically constrained modelling approach and Bayesian analysis method was used to rationalise these measurements showing that the structures are remarkably similar at the air-DES interface to those previously observed at the air-water interface.
This has the important implication that DES, therefore, offer the possibility of performing studies of model membranes in the absence of water.
Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein-membrane interactions and development of new technologies for drug delivery.
However, the PG component did show a significant difference; having a larger head component volume than observed for the same system in water.
This suggests that the transfer of lipids to a DES is not just a simple substitution of the subphase.
In this specific case, we have proposed an explanation based on the dissociation of the PG head component salt and the subsequent interaction with the DES.
Finally, the use of MCMC sampling of the reflectometry model parameter space gives insight into the correlations present in XRR data modelling, that should be considered in nature work of this nature.

@@

\section{Author Contributions}
T.A., A.J.J., A.S.-F. and K.J.E. were involved in the experimental design and conducted the experiments along with R.A.C..
A.R.M. developed the chemically-consistent model and analysed the data, with input from S.C.P, A.S.-F., T.A., and R.A.C..
A.R.M., A.S.-F. and T.A. wrote the manuscript, with input from all authors.

>>>>

\begin{abstract}
In this work, we present the first example of the self-assembly of phospholipid monolayers at the interface between air and an ionic solvent.
Deep eutectic solvents are a novel class of environmentally friendly, non-aqueous, room temperature liquids with tunable properties, that have wide-ranging potential applications and are capable of promoting the self-assembly of surfactant molecules.
We use a chemically-consistent Bayesian modelling of X-ray and neutron reflectometry measurements to show that these monolayers broadly behave as they do on water.
This method allows for the monolayer structure to be determined, alongside the molecular volumes of the individual monolayer components, without the need for water-specific constraints to be introduced.
Furthermore, using this method we are able to better understand the correlations present between parameters in the analytical model.
This example of a non-aqueous phospholipid monolayer has important implications for the potential uses of these solvents and for our understanding of how biomolecules behave in the absence of water.
  \begin{description}
  \item[Usage]
  Electronic Supplementary Information (ESI) available: All analysis/plotting
  scripts and figure files, allowing for a fully reproducible, and automated,
  analysis workflow for the work presented is available at
  \url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.2573512)
  under a CC BY-SA 4.0 license.
  Reduced experimental datasets are available at
  \url{https://doi.org/10.15125/BATH-00548}, under a CC-BY 4.0 license.
  \end{description}
\end{abstract}
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

@@

\subsection{Methods}
%
XRR measurements were taken on I07 at Diamond Light Source, at \SI{12.5}{\kilo\electronvolt} photon energy using the double-crystal deflector \cite{arnold_implementation_2012}.
The reflected intensity was measured in a momentum transfer range from \SIrange{0.018}{0.7}{\per\angstrom}.
The data were normalised with respect to the incident beam and the background was measured from off-specular reflection and subsequently subtracted.
Samples were equilibrated for at least one hour and preserved under an helium atmosphere to minimise the adsorption of water by the subphase.
XRR data were collected for each of the lipids, DLPC, DMPC, DPPC and DMPG at four surface pressures (DLPC: \SIlist[list-units = single]{20;25;30;35}{\milli\newton\per\meter}, DMPC: \SIlist[list-units = single]{20;25;30;40}{\milli\newton\per\meter}, DPPC: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, DMPG: \SIlist[list-units = single]{15;20;25;30}{\milli\newton\per\meter}, as measured with an aluminium Wilhelmy plate; measurements were conducted at \SIlist{7;22}{\celsius}.
The aluminium Wilhelmy plate was used over a traditional paper plate due to the low wettability of paper by the DES.

@@

In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evolution method available to refnx from the scipy library \cite{jones_scipy_2001}, to find the parameters that gave the best fit to the data.
The parameter space was then probed using the MCMC method available through emcee \cite{foreman-mackey_emcee_2013}, which allowed for an estimate of the probability distribution function (PDF) associated with each parameter.
In the MCMC sampling, 200 walkers were used over 1000 iterations, following equilibration of 200 iterations.
The use of MCMC sampling allowed for a Bayesian inference of the PDF for each of the variables and their respective interactions and the Shapiro test to be used to assess if each PDF was normally distributed.
Parameters that were shown to be normally distributed are given with symmetric confidence intervals, while those that failed the Shapiro test are given with asymmetric confidence intervals (\SI{95}{\percent} confidence intervals in both cases).
However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, i.e. they do not account of systematic uncertainty in the measurement that is underrepresented, or unrepresented, in the experimental dataset.

%
\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/dlpc_ref_sld}
    \includegraphics[width=0.45\textwidth]{figures/dmpc_ref_sld}
    \includegraphics[width=0.45\textwidth]{figures/dppc_ref_sld}
    \includegraphics[width=0.45\textwidth]{figures/dmpg_ref_sld}
    \caption{\small The XRR profiles (left) and SLD profiles (right) for each
  of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, and (d) DMPG, at the four
  measured surface pressures; see legend above each plot. The different
  surface pressure XRR profiles have been offset in the $y$-axis by an order
  of magnitude and SLD profiles offset in the $y$-axis by
  \SI{5e-6}{\per\square\angstrom}, for clarity.}
    \label{fig:lipids}
\end{figure}
%
\section{Results \& Discussions}
%
The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid.
Although lipid monolayers on water often reach values above \SI{50}{\milli\newton\per\meter}, signifying a decrease in surface tension to ca. \SI{20}{\milli\newton\per\meter} upon addition of lipid, it was not possible to reach those values for the monolayers on DES \cite{mohwald_phospholipid_1990}.
The surface tension of pure choline chloride:glycerol has been previously reported to be \SI{63.5\pm0.5}{\milli\newton\per\meter} \cite{sanchez-fernandez_micellization_2016}.
This means that a surface pressure of ca. \SI{40}{\milli\newton\per\meter} iin choline chloride:glycerol will also result in a reduction to ca. \SI{20}{\milli\newton\per\meter} in the surface tension.
Interestingly, the absolute values of surface tension in both water and choline chloride:glycerol after addition of lipid are similar.
Therefore, surface pressures of up to \SI{40}{\milli\newton\per\meter} were measured for the monolayers on DES, when possible.
The resulting XRR profiles and associated SLD profiles are shown in Figure \ref{fig:lipids}.
Table \ref{tab:liptab} gives details of all varied parameters for each lipid at \SI{30}{\milli\newton\per\meter}, as well as the details of $\phi_h$ which was determined from Eqn. \ref{equ:phih} (the same details for the other surface pressures are available in Section \ref{sec:xrrpara} of the ESI).
%
\begin{table*}
    \caption{\label{tab:liptab} The best-fit values, and associated \SI{95}{\percent} confidence intervals for the varying parameters in the XRR models, at the \SI{30}{\milli\newton\per\meter}. The values for $\phi_h$ was obtained from the appropriate use of Eqn. \ref{equ:phih}.}
  \begin{ruledtabular}
    \begin{tabular*}{\textwidth}{ccccc}
    Lipid & DLPC & DMPC & DPPC & DMPG \\
    \hline
    $\sigma$/\si{\angstrom} & \input{../output/dlpc/rough30.txt} & \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
    $d_t$/\si{\angstrom} & \input{../output/dlpc/tail30.txt} & \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
    \hline
    $V_t$/\si{\cubic\angstrom} & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
    $V_h$/\si{\cubic\angstrom} & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
    $d_h$/\si{\angstrom} & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} & \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
    \end{tabular*}
  \end{ruledtabular}
\end{table*}
%

Following the initial structural determination of the monolayer by XRR, NR was used to confirm the structure and show the applicability of the chemically-consistent model for DPPC and DMPC.
The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron} (the other NR and SLD profiles can be found in Figure \ref{fig:sineutron} of the ESI).
Table \ref{tab:neutron} gives details of the varied parameters at each surface pressure as well as $\phi_h$ as determined from NR.
%
\begin{figure}
    \centering
  \includegraphics[width=0.45\textwidth]{figures/dmpc_20n_ref_sld}
    \includegraphics[width=0.45\textwidth]{figures/dppc_20n_ref_sld}
    \caption{\small The NR and SLD profiles at a surface pressure of
  20 mNm$^{-1}$ for two contrasts, the solid line identifing the hdDES contrast and the dashed line the hDES contrast; (a) DMPC, (b) DPPC. The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
    \label{fig:neutron}
\end{figure}
%
%
\begin{table*}
  \caption{\label{tab:neutron} The best-fit values, and associated 95 \%
  confidence intervals for the varying parameters in the co-refined NR models.
  The values of $\phi_h$ were found using Eqn. \ref{equ:phih}.}
  \begin{ruledtabular}
    \begin{tabular*}{\textwidth}{ccccc}
    Lipid & \multicolumn{2}{c}{d$_{54}$-DMPC} & \multicolumn{2}{c}{d$_{62}$-DPPC} \\
    SP/mNm$^{-1}$ & 20 & 25 & 15 & 20 \\
    \hline
    $\sigma_{t,h,s}$/\si{\angstrom} & \input{../output/dmpc/rough20_neutron.txt} & \input{../output/dmpc/rough25_neutron.txt} & \input{../output/dppc/rough15_neutron.txt} & \input{../output/dppc/rough20_neutron.txt} \\
    $d_t$/\si{\angstrom} & \input{../output/dmpc/tail20_neutron.txt} & \input{../output/dmpc/tail25_neutron.txt} & \input{../output/dppc/tail15_neutron.txt} & \input{../output/dppc/tail20_neutron.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dmpc/solh20_neutron.txt} & \input{../output/dmpc/solh25_neutron.txt} & \input{../output/dppc/solh15_neutron.txt} & \input{../output/dppc/solh20_neutron.txt} \\
    \end{tabular*}
  \end{ruledtabular}
\end{table*}
%
\subsection{Effect of compression on monolayer thickness}
%
From Tables \ref{tab:liptab} and \ref{tab:neutron}, we can see that, as expected and as found in previous work \cite{mohwald_phospholipid_1990,vaknin_structural_1991}, the thickness of the tail layer increases as the number of carbon atoms in the tail chain increases.
Furthermore, the thickness of the tail layers in these monolayers appears to agree well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\AA\ at 30 mN/m in DES compared with $d_t=15.8$~\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in water for DMPC \cite{johnson_structure_1991}, and \input{../output/dppc/tail30.txt}~\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=16.7$~\si{\angstrom} at \SI{40}{\milli\newton\per\meter} in water for DPPC \cite{helm_phospholipid_1987}.

@@

\subsection{Solvent effect on lipid head component volumes}
%
Figure \ref{fig:lipresults} shows the PDFs determined for the head component volume for each of the four lipids.
The three lipids with the PC head component are consistent, giving values of $\sim330$ \AA$^3$, regardless of tail component.
This agrees well with the values found for the same head component in water, shown in Table \ref{tab:water}.
Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}~\si{\angstrom\cubed}.
The PG head component volume in water, from either DMPG using differential vibrating tube densimetry \cite{pan_molecular_2012} or POPG using molecular dynamics simulations \cite{kucerka_scattering_2012}, is noticeably smaller.
This indicates that there may be some effect arising from the solvation in choline chloride:glycerol causing an apparent increase in the PG component volume when compared with water.
However, this has only been shown for a single PG-lipid at the air–DES interface.

@@

A physically and chemically constrained modelling approach and Bayesian analysis method was used to rationalise these measurements showing that the structures are remarkably similar at the air-DES interface to those previously observed at the air-water interface.
This has the important implication that DES, therefore, offer the possibility of performing studies of model membranes in the absence of water.
Such applications may include fundamental investigations of phospholipid monolayers in extreme environments (total or partial absence of water, cryogenic temperatures), protein-membrane interactions and development of new technologies for drug delivery.
However, the PG component did show a significant difference; having a larger head component volume than observed for the same system in water.
This suggests that the transfer of lipids to a DES is not just a simple substitution of the subphase.
In this specific case, we have proposed an explanation based on the dissociation of the PG head component salt and the subsequent interaction with the DES.
Finally, the use of MCMC sampling of the reflectometry model parameter space gives insight into the correlations present in XRR data modelling, that should be considered in work of this nature.

@@

\section{Author Contributions}
T.A., A.J.J., A.S.-F. and K.J.E. were involved in the experimental design and conducted the experiments along with R.A.C..

A.R.M. developed the chemically-consistent model and analysed the data, with input from S.C.P, A.S.-F., T.A., and R.A.C..

A.R.M., A.S.-F. and T.A. wrote the manuscript, with input from all authors.
